Formalizing Stack Safety as a Security Property

### 2022-10-10 submission5/noexceptions.tex
Delete random comment

\apt{Remainder of this section is on the right track, but needs some expansion,
  and to be tied back more clearly and consistently to the examples. I started
  word-smithing this first para...}
We treat confidentiality as a form of non-interference as well: the confidentiality of a caller
means that its callee's behavior is dependent only on publicly visible data,
not the caller's private state. As we saw in the examples, we must consider both the observable events
that the callee produces during the call and the changes that the callee makes to the state that might
affect the caller after the callee returns.

>>>>

We treat confidentiality as a form of non-interference as well: the confidentiality of a caller
means that its callee's behavior is dependent only on publicly visible data,
not the caller's private state. As we saw in the examples, we must consider both the observable events
that the callee produces during the call and the changes that the callee makes to the state that might
affect the caller after the callee returns.
